BivData Setup

### 2020-02-03 doc/Bivalent_Analysis.Rmd
too much work from home

```{r clean.biv.data4.MM, echo=FALSE}

@@

@@

mouse.avs_4MM <- ddply(Curated_BivData, c("mouse"), summarise,
                        Nmice = length(unique(mouse)),
                        Ncells  = length(Obj.ID),
                        mean_SC = as.numeric(format(round(  mean(chromosomeLength), 3 ), nsmall=3) ),
                        cV = cv(chromosomeLength),
                        var = as.numeric(format(round(   var(chromosomeLength),3), nsmall=3) ),
                        sd   = round(sd(chromosomeLength), 3),
                        se   = round(sd / sqrt(Ncells), 3),

@@

@@

@@

@@

@@

@@

Prediction, High rec males have longer SC.

@@

@@

>>>>

```{r biv.data_table.4MM.HetC, echo=FALSE}

@@

#I'd like to merge the additional strains used for the male tests

@@

mouse.avs_4MM <- ddply(Curated_BivData, c("mouse"), summarise,
                        Nmice = length(unique(mouse)),
                        Ncells  = length(Obj.ID),

                      # mean_CO = mean()

                        mean_SC = as.numeric(format(round(  mean(chromosomeLength), 3 ), nsmall=3) ),
                        cV = cv(chromosomeLength),
                        var = as.numeric(format(round(   var(chromosomeLength),3), nsmall=3) ),
                        sd   = round(sd(chromosomeLength), 3),
                        se   = round(sd / sqrt(Ncells), 3),

@@

#code intp chr

@@

```{r biv.data_table.4MM.Male, echo=FALSE}
#remove female, 
#add back in the BIVDATA from strains which were  removed for the sex-specific comparisons

#Curated_BivData_male

male.av_4MM <- ddply(Curated_BivData_male, c("mouse"), summarise,
                        Nmice = length(unique(mouse)),
                        Ncells  = length(Obj.ID),

                      # mean_CO = mean()

                        mean_SC = as.numeric(format(round(  mean(chromosomeLength), 3 ), nsmall=3) ),
                        cV = cv(chromosomeLength),
                        var = as.numeric(format(round(   var(chromosomeLength),3), nsmall=3) ),
                        sd   = round(sd(chromosomeLength), 3),
                        se   = round(sd / sqrt(Ncells), 3),

#vari
male.av_4MM <- add_sex(male.av_4MM)
male.av_4MM <- add_strain(male.av_4MM)
male.av_4MM <- add_subsp(male.av_4MM)
male.av_4MM <- add_category(male.av_4MM)

#unordered for the mixed models (move this to the MM blocks...?)
#keep order for the plots?
male.av_4MM$subsp <- factor(male.av_4MM$subsp, ordered = FALSE)
male.av_4MM$sex <- factor(male.av_4MM$sex, ordered = FALSE)
male.av_4MM$strain <- factor(male.av_4MM$strain, ordered = FALSE)

@@

Rerun all these predictions for MSM > MOLF as well

@@

APRIL, consider moving these strain chunks to the bivData set up

@@

#### male strain comparisons

```{r male.sc.length.strain, echo=FALSE}

Curated_BivData <- add_species(Curated_BivData)
#isolate all musc
Curated_BivData_male <- Curated_BivData[Curated_BivData$sex == "male",]

#make table
SC.Length.male_table <- ddply(Curated_BivData_male, c("strain"), summarise,
                             mean_SC = mean(chromosomeLength),
                              n_SC = length(Obj.ID),

```{r SC.length.male_tests, echo=FALSE}

## run the tests to check following expectations

#1.Dom strains not different from ech other
#2. PWD and SKIVE are different from the other strains
#3.MSM and MOLF are different from each other

#decide between lm or glm..?
#mouse avs, males

male.Dom.mouse.av <- mouse.avs_4MM[ (mouse.avs_4MM$sex == "male") & (mouse.avs_4MM$subsp == "Dom"), ]
#the subsp labels get messed up, unless they are designated chr first
male.Musc.mouse.av <- mouse.avs_4MM[ (mouse.avs_4MM$sex == "male") & (mouse.avs_4MM$subsp == 2), ]

mouse.avs_4MM$subsp <- as.character(mouse.avs_4MM$subsp)
mouse.avs_4MM$subsp <- ifelse(grepl("MSM", mouse.avs_4MM$strain), "Mol", 
        ifelse(grepl("MOLF", mouse.avs_4MM$strain), "Mol", mouse.avs_4MM$subsp))
male.Mol.mouse.av <- mouse.avs_4MM[ (mouse.avs_4MM$sex == "male") & (mouse.avs_4MM$subsp == "Mol"), ]

Dom.male_SC.length_lm <- lm(mean_SC~ strain,  data =male.Dom.mouse.av  )

Dom.male_SC.length_lm.1 <- lm(mean.SC_1CO~ strain/mouse,  data =male.Dom.mouse.av  )
Dom.male_SC.length_lm.2 <- lm(mean.SC_2CO~ strain,  data =male.Dom.mouse.av  )
#Dom.male_SC.length_lm.3 <- lm(mean.SC_3CO~ strain,  data =male.Dom.mouse.av  ) #only WSB and LEW?
#total sc sig, 1CO sig, 2CO sig

Dom.male_SC.aov <- aov(mean_SC ~ strain, data = male.Dom.mouse.av)
#0.000369 ***

Dom.male_1CO_SC.aov <- aov(mean.SC_1CO ~ strain, data = male.Dom.mouse.av)
#0.000816 ***

Dom.male_2CO_SC.aov <- aov(mean.SC_2CO ~ strain, data = male.Dom.mouse.av)
#0.0148 *

show.Dom.male.SC <- ggplot(male.Dom.mouse.av, aes(y= mean_SC, x= strain, color=strain))+ geom_jitter()

show.Dom.male.SC <- ggplot(male.Dom.mouse.av, aes(y= mean.SC_2CO, x= strain, color=strain))+ geom_jitter()
#making plots above show that mouse average SC lengths are lower could there be microscope issue?

#make sure to remove some of the juvi mice!! from the AP_mouse table

show.Dom.male.CO <- ggplot(
AP_mouse_table_w.Ages[(AP_mouse_table_w.Ages$sex.x == "male") & (AP_mouse_table_w.Ages$subsp.x == "Dom"),], aes(y= mean_co, x= strain.x, color=strain.x))+ geom_jitter()

Dom.male_CO.aov <- aov(mean_co ~ strain, data = AP_mouse_table.HQ[(AP_mouse_table.HQ$sex == "male") & (AP_mouse_table.HQ$subsp == "Dom"),])
#P not sig for CO mean

#seems like there are more mice in the MLH1 data set than bivData
#

#WSB all dissected and imaged in '15
#G imaged 15 - 16
#LEW imaged 15 to 17

ggboxplot(data = male.Dom.mouse.av, x = "strain", y = "mean_SC", 
          color = "strain", palette = c("#00AFBB", "#E7B800", "#FC4E07"),
          ylab = "", xlab = "")

show.Dom.male.SC <- ggplot(male.Dom.mouse.av, aes(y= mean_SC, x= strain, color=strain))+ geom_jitter()

ggboxplot(data = male.Dom.mouse.av, x = "strain", y = "mean_SC", 
          color = "strain", palette = c("#00AFBB", "#E7B800", "#FC4E07"),
          ylab = "", xlab = "")

ggboxplot(data = male.Dom.mouse.av, x = "strain", y = "mean.SC_1CO", 
          color = "strain", palette = c("#00AFBB", "#E7B800", "#FC4E07"),
          ylab = "1CO SC Length", xlab = "")

ggboxplot(data = male.Dom.mouse.av, x = "strain", y = "mean.SC_2CO", 
          color = "strain", palette = c("#00AFBB", "#E7B800", "#FC4E07"),
          ylab = "2CO SC Length", xlab = "")
```

```{r SC.length.pairwise.T, echo=FALSE}
#male.Dom.mouse.av, male.Mol.mouse.av, male.Musc.mouse.av

male.Musc.mouse.av <- male.av_4MM[(male.av_4MM$subsp == "Musc")&(male.av_4MM$sex == "male"),]

Pwise.ttest_Dom.male <- pairwise.t.test(male.Dom.mouse.av$mean_SC, male.Dom.mouse.av$strain)
#G-WSB is sig, WSB-LEW are slightly sig

Pwise.ttest_Musc.male <- pairwise.t.test(male.Musc.mouse.av$mean_SC, male.Musc.mouse.av$strain)
#PWD and MSM are most diff from SKIVE?

Pwise.ttest_Mol.male <- pairwise.t.test(male.Mol.mouse.av$mean_SC, male.Mol.mouse.av$strain)
#the pooled SC value tests are sig

#the mol comparisons are different due to adj p values

Pwise.ttest_Dom.male.1CO <- pairwise.t.test(male.Dom.mouse.av$mean.SC_1CO, male.Dom.mouse.av$strain)
#G-WSB is sig, WSB-LEW are slightly sig

Pwise.ttest_Musc.male.1CO <- pairwise.t.test(male.Musc.mouse.av$mean.SC_1CO, male.Musc.mouse.av$strain)
#no sig (only 3) -- does include CZECCH

#non-sig, with mol pooled with musc

Pwise.ttest_Mol.male.1CO <- pairwise.t.test(male.Mol.mouse.av$mean.SC_1CO, male.Mol.mouse.av$strain)

Pwise.ttest_Dom.male.2CO <- pairwise.t.test(male.Dom.mouse.av$mean.SC_2CO, male.Dom.mouse.av$strain)

Pwise.ttest_Musc.male.2CO <- pairwise.t.test(male.Musc.mouse.av$mean.SC_2CO, male.Musc.mouse.av$strain)
#non of these sig with the mulitple adjust

Pwise.ttest_Mol.male.2CO <- pairwise.t.test(male.Mol.mouse.av$mean.SC_2CO, male.Mol.mouse.av$strain)

pairwise.t.test(Ozone, Month, p.adj = "bonf")

If I want to try to use mouse nested in strain -- I should use cell level metrics (but those have there own flaws)

Ideas for the above 3 tests,

1. no difference in DOM
- no sig logistic regression test
- glm, strain effect?

@@

(merge this with the code above)
Prediction, High rec males have longer SC.

@@

```{r male.IFD_strain, echo=FALSE}

#make table
Musc_male_IFD_table <- ddply(Curated_BivData_male[Curated_BivData_male$hand.foci.count == 2,], c("strain"), summarise,

                        n_obs = length(Obj.ID),
                         mean_IFD = mean(IFD1_ABS, na.rm=TRUE),
                        mean_IFD.nrm = mean(IFD1_PER,na.rm=TRUE)
                         )

        #           mean.SC_0CO = mean(chromosomeLength[which(hand.foci.count == 0)], na.rm = TRUE),
         #         n_0CO =  sum((hand.foci.count == 0), na.rm = TRUE ),
                 # CO2 = sum(hand.foci.count == 2, na.rm=TRUE),

      #             mean.SC_1CO = mean(chromosomeLength[which(hand.foci.count == 1)], na.rm = TRUE),
      #              n_1CO = sum((hand.foci.count == 1), na.rm = TRUE),

      #             mean.SC_2CO = mean(chromosomeLength[which(hand.foci.count == 2)], na.rm = TRUE),
      #             n_2CO = sum((hand.foci.count == 2), na.rm = TRUE),

      #            mean.SC_3CO = mean(chromosomeLength[which(hand.foci.count == 3)], na.rm = TRUE),
      #            n_3CO = sum((hand.foci.count == 3), na.rm = TRUE)

@@

```{r male.Nrm1CO_strain, echo=FALSE}

#isolate all musc
Curated_BivData_male <- Curated_BivData[Curated_BivData$sex == "male",]

#make table
Musc_male_1COpos_table <- ddply(Curated_BivData_male[Curated_BivData_male$hand.foci.count == 1,], c("strain"), summarise,

                        n_obs = length(Obj.ID),
                         mean_F1 = mean(Foci1, na.rm=TRUE),
                        mean_F1.nrm = mean(PER_Foci_1,na.rm=TRUE)

        #           mean.SC_0CO = mean(chromosomeLength[which(hand.foci.count == 0)], na.rm = TRUE),
         #         n_0CO =  sum((hand.foci.count == 0), na.rm = TRUE ),
                 # CO2 = sum(hand.foci.count == 2, na.rm=TRUE),

      #             mean.SC_1CO = mean(chromosomeLength[which(hand.foci.count == 1)], na.rm = TRUE),
      #              n_1CO = sum((hand.foci.count == 1), na.rm = TRUE),

      #             mean.SC_2CO = mean(chromosomeLength[which(hand.foci.count == 2)], na.rm = TRUE),
      #             n_2CO = sum((hand.foci.count == 2), na.rm = TRUE),

      #            mean.SC_3CO = mean(chromosomeLength[which(hand.foci.count == 3)], na.rm = TRUE),
      #            n_3CO = sum((hand.foci.count == 3), na.rm = TRUE)

### 2020-02-03 doc/Main_Report_Results.rmd
too much work from home

setwd("~./MLH1repo/")

load(file="~./MLH1repo/data/MLH1_data_setup_1.5.20.RData")
load(file="/data/CleanBivData_1.28.20.RData")

@@

```{r HQ.MixedModel.1, echo=FALSE, digits = 2}
#table(DF.HetC.MixedModel$strain, DF.HetC.MixedModel$sex)
#mean_co.HQ  (this might remove some of the MOLF males)

@@

@@

#ranef(HetC.MixedModel.HQ.var_co)
```

@@

Q12_mouse_table_w.Ages$subsp <- ifelse(grepl("MSM", Q12_mouse_table_w.Ages$strain), "Mol", 
        ifelse(grepl("MOLF", Q12_mouse_table_w.Ages$strain), "Mol", NA))

@@

M1.Q12_var_co <- lme( var ~ subsp * sex, data=Q12_mouse_table_w.Ages, random=list(strain=pdDiag(~sex) ) )

as.data.frame( round(summary(M1.Q12_var_co)$tTable, 6))

@@

```{r cV.models, echo=FALSE}
HQjust.strain.var <- lme(var ~ subsp * sex, data=DF.HetC.MixedModel.HQ, random = ~1|strain)

as.data.frame( round(summary(HQjust.strain.var)$tTable, 6))

#summary(HQjust.strain.var_co)
```

$$mouse .var CO ~=~ subsp * sex  + \varepsilon$$
```{r base.var.mol, echo=FALSE, eval=FALSE}
HetC.MixedModel.mol.var_co <- lme(var ~ subsp * sex, data=DF.HetC.MixedModel.HQ.mol, random=list(strain=pdDiag(~sex) ) )

as.data.frame( round(summary(HetC.MixedModel.mol.var_co)$tTable, 6))

@@

$$mouse .var CO ~=~ subsp * sex + rand(strain * sex) + \varepsilon$$
```{r var.model.1, echo=FALSE, eval=FALSE}
#main cV.CO
HetC.MixedModel.varco <- lme(var ~ subsp * sex, data=DF.HetC.MixedModel, random=list(strain=pdDiag(~sex) ) )

as.data.frame( round(summary(HetC.MixedModel.varco)$tTable, 6))

#summary(HetC.MixedModel.cVco)
#ranef(HetC.MixedModel.cVco)
```

```{r var.contrast, echo=FALSE, eval=FALSE}
#contrast models
# review this logic again

full2strain.CV <- anova(HetC.MixedModel.varco, just.strain.var_co)#0.9997

@@

@@

chrm.class.DF = read.csv("C:/Users/alpeterson7/Documents/MLH1repo/data/ChrmClassProportions2.csv", header = TRUE)

@@

```{r DMC1.setup, echo=FALSE}
#load DMC1 csv
DMC1.DF <- read.csv("~./DMC1/newJuviQuant.csv", header = TRUE)
DMC1.DF$fileName <- DMC1.DF$Original.Name
DMC1.DF <- add_mouse(DMC1.DF)
DMC1.DF <- add_strain(DMC1.DF)
DMC1.DF <- add_category(DMC1.DF)
DMC1.DF <- add_subsp(DMC1.DF)
DMC1.DF <- DMC1.DF[DMC1.DF$stage != "P",]

@@

```{r normality, echo=FALSE, warning=FALSE}
#histograms for each

@@

```{r DMC1.plot, echo=FALSE, warning=FALSE}
#think of better color scheme
#make the jitter col thinner or make the stacked dots.
#remember that box-plots add outlier dots.
#change y labels

@@

```{r DMC1_MLH1.cor, echo=FALSE}
#make category averages from AP_mouse_table.HQ
mean.MLH1.obs <- ddply(.data=AP_mouse_table.HQ,
                 .(category),
                 summarize, 
                 mean.MLH1 = mean(mean_co),
                 var.MLH1 = var(mean_co)
)

@@

The correlation with MLH1 and leptotene cells is `r MLH1.DMC1.L_cor`.

The correlation with MLH1 and zygotene cells is `r MLH1.DMC1.Z_cor`.

@@

```{r trackcurBivData, echo=FALSE}
#list / tally of current curated Bivdata
Cur_biv = read.csv("~./MLH1repo/data/CurrentCuratedDataset_13.1.20.csv", header = TRUE)

```{r barlett.test, echo=FALSE}

```{r DMC1_anova, echo=FALSE, warning=FALSE}
#1. ANOVA, is there a difference in DMC1 counts across strains?
mod.L <- lm(total.count ~ strain, data = DMC1.DF[DMC1.DF$stage == "L",])
mod.Z <- lm(total.count ~ strain, data = DMC1.DF[DMC1.DF$stage == "Z",])

```{r DMC1_t.tests, echo=FALSE, warning=FALSE}
#2. t-tests for the DMC1 counts 
#need to account for sample sizes when comparing t.tests (KAZ and G don't have equal across )
#best case scnario -- more microscoping to get ~20 cells for each stage by strain combo

Divide the Musculus strains into high and low recombining groups to characterize the difference in distributions. The p-values from the t.tests of the high vs low groups, indicate that the high recombining are significantly higher for the L cells (p value = `r ttest.HighLow.L$p.value`) while the Z cells, there is not a significant difference across the high and low groups (value = `r ttest.HighLow.Z$p.value`).

@@

```{r mouse.specific.Qplot, echo=FALSE, message=FALSE, results='hide', warning=TRUE, include=FALSE, eval=FALSE}
#### Distributions by mouse
#There are code chunks that make a big dfs of CO count by quality score plot. The #code has been commented out, and moved to it's own doc.

@@

>>>>

#setwd("~./MLH1repo/")

load(file = "C:/Users/April/Documents/MLH1repo/data/MLH1/MLH1_data_setup_1.31.20.RData")

#2.2.20

load(file="C:/Users/April/Documents/MLH1repo/data/CleanBivData_1.27.20.RData")

#load(file="~./MLH1repo/data/MLH1_data_setup_1.5.20.RData")

@@

```{r M1_HQ.MixedModel.1, echo=FALSE, digits = 2}
#table(DF.HetC.MixedModel$strain, DF.HetC.MixedModel$sex)
#mean_co.HQ  (this might remove some of the MOLF males)

@@

## Musc Males

test a model for fixed effects of strains within musc. The purpose is to distinguihsi musc strains from low 'Dom' level strains.

```{r Musc.male.Model.data.setup, echo=FALSE}
#nested mouse in strain

#remove the extra merged cols
Musc.male_mouse.av <- subset(AP_mouse_table_w.Ages, select= -c(sex.y,sex.x,
                            subsp.y,subsp.x,
                    category.y,category.x, strain.x,
                    strain.y, mouse.1  )  )

Musc.male_mouse.av <- add_strain(Musc.male_mouse.av)
Musc.male_mouse.av <- add_sex(Musc.male_mouse.av)
Musc.male_mouse.av <- add_subsp(Musc.male_mouse.av)
Musc.male_mouse.av <- add_species(Musc.male_mouse.av)

Musc.male_mouse.av$subsp <- as.character(Musc.male_mouse.av$subsp)

Musc.male_mouse.av$subsp[Musc.male_mouse.av$strain== "MSM"] <- 'Mol'
Musc.male_mouse.av$subsp[Musc.male_mouse.av$strain== "MOLF"] <- "Mol"

#use original for getting the other strains

Musc.male_mouse.av <- Musc.male_mouse.av[Musc.male_mouse.av$species == "M.musculus",]
Musc.male_mouse.av <- Musc.male_mouse.av[Musc.male_mouse.av$subsp == "Musc",]
Musc.male_mouse.av <- Musc.male_mouse.av[Musc.male_mouse.av$sex == "male",]

#set the factors
Musc.male_mouse.av$strain <- factor(Musc.male_mouse.av$strain, ordered = FALSE)
Musc.male_mouse.av$mouse <- factor(Musc.male_mouse.av$mouse, ordered = FALSE)

#compare the the higher quality plots
#Q1Q2

Q12_mouse_table_w.Ages <- add_subsp(Q12_mouse_table_w.Ages)
Q12_mouse_table_w.Ages <- add_species(Q12_mouse_table_w.Ages)

Q12_mouse_table_w.Ages$subsp <- as.character(Q12_mouse_table_w.Ages$subsp)

Q12_mouse_table_w.Ages$subsp[Q12_mouse_table_w.Ages$strain== "MSM"] <- 'Mol'
Q12_mouse_table_w.Ages$subsp[Q12_mouse_table_w.Ages$strain== "MOLF"] <- "Mol"

Musc.male.Q12 <- Q12_mouse_table_w.Ages[(Q12_mouse_table_w.Ages$subsp == "Musc")&(Q12_mouse_table_w.Ages$sex == "male"),]

Musc.male.Q12$strain <- factor(Musc.male.Q12$strain, ordered = FALSE)
Musc.male.Q12$mouse <- factor(Musc.male.Q12$mouse, ordered = FALSE)

#Q123  Q123_mouse_table

Q123_mouse_table <- add_subsp(Q123_mouse_table)
Q123_mouse_table <- add_species(Q123_mouse_table)

Q123_mouse_table$subsp <- as.character(Q123_mouse_table$subsp)

Q123_mouse_table$subsp[Q123_mouse_table$strain== "MSM"] <- 'Mol'
Q123_mouse_table$subsp[Q123_mouse_table$strain== "MOLF"] <- "Mol"

Musc.male.Q123 <- Q123_mouse_table[(Q123_mouse_table$subsp == "Musc")&(Q123_mouse_table$sex == "male"),]

Musc.male.Q123$strain <- factor(Musc.male.Q123$strain, ordered = FALSE)
Musc.male.Q123$mouse <- factor(Musc.male.Q123$mouse, ordered = FALSE)

```{r Musc.male.show.plots, echo=FALSE}

musc.male.plot <- ggplot(Musc.male_mouse.av, aes(color= strain))+geom_jitter(aes(x = as.factor(strain), y = mean_co, color= strain, alpha=0.5), width = .2 )+ ggtitle("Musc male of MLH1 distributions")+scale_color_manual(values=colors_of_strains)

# + theme(axis.title.x=element_blank(),
#        axis.text.x=element_blank(),
#        axis.ticks.x=element_blank()) +

#ylim( c((min(MLH1_data$adj_nMLH1.foci)-3) ), (max(MLH1_data$adj_nMLH1.foci)+3)) +  
musc.male.plot

Q123.musc.male.plot <- ggplot(Musc.male.Q123,
                             aes(color= strain))+geom_jitter(aes(x = as.factor(strain), y = mean_co, color= strain, alpha=0.5), width = .2 )+ ggtitle("Q123 Musc male of MLH1 distributions")+scale_color_manual(values=colors_of_strains)

Q123.musc.male.plot
#THE q12,data set only 
#Q123 has 5 strain rep (no TOM), there are still some mouse outliers

This is the table and plot of new Musc strains

`r kable(table( droplevels( Musc.male_mouse.av$strain)  ))`

Given the plot, make note of the potential outlier mice.  The strains have unequal variance

KAZ: 10jul19_KAZ_m3, 10jul19_KAZ_m1, 10jul19_KAZ_m2

PWD: 24sep14_PWD_m1, 18may15_PWD_m1?

```{r M1_Musc.male, echo=FALSE}

#mouse.av ~ mouse | strain

#not sure the right syntax for nested factors
#Musc.male.M1 <- lm(mean_co ~ (mouse|strain), data=Musc.male_mouse.av )

Musc.male.M1 <- lm(mean_co ~ strain, data=Musc.male_mouse.av )

as.data.frame(  round(summary(Musc.male.M1)$coefficients, 4) )

#all of the strain have a significant effect agaisnt the group mean / intercept
#looking at the intercept -- the PWD observations are pushing up the average

#musc male Q123  Q123_mouse_table

Musc.male.Q123.M1 <- lm(mean_co ~ strain, data=Musc.male.Q123 )

as.data.frame(  round(summary(Musc.male.Q123.M1)$coefficients, 4) )

#mostly all strains, (but SKIVE) are significant -- similar to the top model

#shoul I compare with subsampling

```{r Musc.male.M2}

#mouse.av ~ strain

@@

#ranef(HetC.MixedModel.HQ.var_co)

#CV
M1.cv_co <- lme( cV ~ subsp * sex, data=DF.HetC.MixedModel.HQ, random=list(strain=pdDiag(~sex) ) )

#summary(HetC.MixedModel.HQ.var_co)
as.data.frame( round(summary(M1.cv_co)$tTable, 6))
```

@@

#need to change to chr first

Q12_mouse_table_w.Ages$subsp <- as.character(Q12_mouse_table_w.Ages$subsp)

Q12_mouse_table_w.Ages$subsp[Q12_mouse_table_w.Ages$strain== "MSM"] <- 'Mol'

Q12_mouse_table_w.Ages$subsp[Q12_mouse_table_w.Ages$strain== "MOLF"] <- "Mol"

@@

M1.Q12_var <- lme( var ~ subsp * sex, data=Q12_mouse_table_w.Ages, random=list(strain=pdDiag(~sex) ) )

as.data.frame( round(summary(M1.Q12_var)$tTable, 6))

M1.Q12_CV <- lme( cV ~ subsp * sex, data=Q12_mouse_table_w.Ages, random=list(strain=pdDiag(~sex) ) )

as.data.frame( round(summary(M1.Q12_CV)$tTable, 6))

@@

```{r M2.var, echo=FALSE}
#this model must be the same as M! -- since all the results are the same
M2.var <- lme(var ~ subsp * sex, data=DF.HetC.MixedModel.HQ, random = ~1|strain)

as.data.frame( round(summary(M2.var)$tTable, 6))

#summary(HQjust.strain.var_co)

M2.CV <- lme(cV ~ subsp * sex, data=DF.HetC.MixedModel.HQ, random = ~1|strain)

as.data.frame( round(summary(M2.CV)$tTable, 6))

@@

```{r M2.var.Q12, echo=FALSE}
M2.Q12_var_co <- lme(var ~ subsp * sex, data=Q12_mouse_table_w.Ages, random = ~1|strain)

as.data.frame( round(summary(M2.Q12_var_co)$tTable, 6))

M2.Q12_CV <- lme(cV ~ subsp * sex, data=Q12_mouse_table_w.Ages, random = ~1|strain)

as.data.frame( round(summary(M2.Q12_CV)$tTable, 6))
```

$$mouse .var CO ~=~ subsp * sex  + \varepsilon$$
```{r M3.var, echo=FALSE, eval=FALSE}
M3.var <- lm(var ~ subsp * sex * strain, data=DF.HetC.MixedModel.HQ)
as.data.frame( round(summary(M3.var)$tTable, 6))

M3.cv <- lm(cV ~ subsp * sex * strain, data=DF.HetC.MixedModel.HQ)
as.data.frame( round(summary(M3.cv)$tTable, 6))
#these models won't work
```

```{r M3VAR.Q12, echo=FALSE, eval=FALSE}
#ugh, don't know how to get these to work 
M3.Q12_var <- glm(var ~ subsp * sex * strain, data=Q12_mouse_table_w.Ages)

as.data.frame(summary(M3.Q12_var)$tTable, 6)
#results don't show

M3.Q12_cv <- lm(cv ~ subsp * sex * strain, data=Q12_mouse_table_w.Ages)

as.data.frame( round(summary(M3.Q12_cv)$tTable, 6))
```

```{r M4.var, echo=FALSE, eval=FALSE}
M4.var <- lm(var ~ sex * strain, data=DF.HetC.MixedModel.HQ)

as.data.frame( round(summary(M4.var)$tTable, 6))

M4.cv <- lm(cV ~ sex * strain, data=DF.HetC.MixedModel.HQ)

as.data.frame( round(summary(M4.cv)$tTable, 6))
```

```{r M4.var_Q12, echo=FALSE, eval=FALSE}

M4.var_Q12 <- lm(var ~ sex * strain, data=Q12_mouse_table_w.Ages)
as.data.frame( round(summary(M4.var_Q12)$tTable, 6))

#these results not print / working
M4.CV_Q12 <- lm(cV ~ sex * strain, data=Q12_mouse_table_w.Ages)
as.data.frame( round(summary(M4.CV_Q12)$tTable, 6))
```

$$mouse .var CO ~=~ subsp * sex + rand(strain * sex) + \varepsilon$$

```{r var.contrast, echo=FALSE, eval=FALSE}
#contrast models -- what's the points for this block
# review this logic again
full2strain.CV <- anova(HetC.MixedModel.varco, just.strain.var_co)#0.9997

@@

I couldn't get many of the models to return results.

@@

chrm.class.DF = read.csv("~./MLH1repo/data/ChrmClassProportions2.csv", header = TRUE)

#chrm.class.DF = read.csv("C:/Users/alpeterson7/Documents/MLH1repo/data/ChrmClassProportions2.csv", header = TRUE)

@@

```{r DMC1.setup, echo=FALSE, eval=FALSE}
#load DMC1 csv
DMC1.DF <- read.csv("~./DMC1/newJuviQuant.csv", header = TRUE)

DMC1.DF$fileName <- DMC1.DF$Original.Name
DMC1.DF <- add_mouse(DMC1.DF)
DMC1.DF <- add_strain(DMC1.DF)
DMC1.DF <- add_category(DMC1.DF)
DMC1.DF <- add_subsp(DMC1.DF)
DMC1.DF <- DMC1.DF[DMC1.DF$stage != "P",]

@@

```{r normality, echo=FALSE, warning=FALSE, eval=FALSE}
#histograms for each

@@

```{r DMC1.plot, echo=FALSE, warning=FALSE, eval=FALSE}
#think of better color scheme
#make the jitter col thinner or make the stacked dots.
#remember that box-plots add outlier dots.
#change y labels

@@

```{r DMC1_MLH1.cor, echo=FALSE, eval=FALSE}
#make category averages from AP_mouse_table.HQ
mean.MLH1.obs <- ddply(.data=AP_mouse_table.HQ,
                 .(category),
                 summarize, 
                 mean.MLH1 = mean(mean_co),
                 var.MLH1 = var(mean_co)
)

@@

The correlation with MLH1 and leptotene cells is r MLH1.DMC1.L_cor.

The correlation with MLH1 and zygotene cells is r MLH1.DMC1.Z_cor.

# Single Bivalent Patterns

@@

@@

```{r mouse.specific.Qplot, echo=FALSE, message=FALSE, results='hide', warning=TRUE, include=FALSE, eval=FALSE}

#REMOVE This BLOCK?

#### Distributions by mouse
#There are code chunks that make a big dfs of CO count by quality score plot. The #code has been commented out, and moved to it's own doc.

@@

```{r trackcurBivData, echo=FALSE, eval=FALSE}
#REMOVE THIS BLOCK??

#list / tally of current curated Bivdata

Cur_biv = read.csv("~./MLH1repo/data/CurrentCuratedDataset_13.1.20.csv", header = TRUE)

```{r barlett.test, echo=FALSE, eval=FALSE}

```{r DMC1_anova, echo=FALSE, warning=FALSE, eval=FALSE}
#1. ANOVA, is there a difference in DMC1 counts across strains?
mod.L <- lm(total.count ~ strain, data = DMC1.DF[DMC1.DF$stage == "L",])
mod.Z <- lm(total.count ~ strain, data = DMC1.DF[DMC1.DF$stage == "Z",])

```{r DMC1_t.tests, echo=FALSE, warning=FALSE, eval=FALSE}
#2. t-tests for the DMC1 counts 
#need to account for sample sizes when comparing t.tests (KAZ and G don't have equal across )
#best case scnario -- more microscoping to get ~20 cells for each stage by strain combo

Divide the Musculus strains into high and low recombining groups to characterize the difference in distributions. The p-values from the t.tests of the high vs low groups, indicate that the high recombining are significantly higher for the L cells (p value = r ttest.HighLow.L$p.value) while the Z cells, there is not a significant difference across the high and low groups (value = r ttest.HighLow.Z$p.value).

### 2020-02-03 src/BivData_Setup.Rmd
added todo note
notes on IFD and sis-co-ten patterns
small bit of work
too much work from home

test work from home ()

@@

@@

>>>>

test work from home (),

- remove BivData! (these are all Peromyscus!!)

calq the nromalized.siscoten, double check the negative values; 13sep18_28jun18_MOLF_m1_sp1_18.1_rev_14, 27aug15_12jun15_WSB_m2_sp1_18_rev_18, 21nov17_16nov17_MSM_f3_sp1_3_rev_1

foci.pass = 2  5aug17_14jul17_MSM_f1_sp1_13_rev_3

hand foci =0 but there is a foci position

too high hand foci count

declare the Strain specific BivData_DFs  (for convinice)

@@

```{r no.Foci.Pos, echo=FALSE}

just.SC.length <- Curated_BivData[is.na(Curated_BivData$hand.foci.count),]#650 lines

#table(just.SC.length$category)
#decide what to do with these lines
#how will they be represented in Mat Methods?

@@

```{r Q1Q2.mouse.table, echo=FALSE}
